Environmental pathogen reservoirs and habitat heterogeneity in a metapopulation

### 2014-07-08 Manuscript/manuscript.tex
Methods edits
Edits to methods section addressing comments from Colleen; trying to
clarify model structure, different parameterizations used, and the
different simulation studies performed.

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{lineno}
\usepackage{hyperref}

@@

Many wildlife diseases are caused by pathogens that can persist, and remain infectious, for long periods of time in the environment.  Examples include chronic wasting disease (\cite{Miller2006}), anthrax (\cite{Dragon1995}), plague (\cite{Eisen2008}), and white nose syndrome (\cite{Lindner2011}), among others.  This environmental persistence creates environmental pathogen reservoirs from which hosts can become infected without direct contact with an infectious individual.  This additional transmission pathway can have important consequences for disease dynamics, with models showing that increased environmental persistence generally facilitates increased pathogen persistence and spread relative to direct transmission alone (\cite{Almberg2011}, \cite{Sharp2011}, \cite{Breban2009}.

@@

\subsection{Model Structure}
To address the above questions, we developed a theoretical stochastic patch occupancy model (SPOM) in which each patch can be in one of three possible states: occupied by susceptible hosts (S), occupied by infectious hosts (I), unoccupied by the host, but with an infectious pathogen reservoir, and unoccupied by both host and pathogen.  State transitions are governed by host colonization, extinction, and infection rates, where a susceptible population can become infectious either through direct contact with infectious immigrants, or through a local pathogen reservoir.

@@

The extinction rate of patch $i$ in state $X$ is given by:
\begin{equation}
E_{Xi}=\frac{e_X}{A_i^\alpha},
\end{equation}
where $e_X$ is the extinction rate of a patch of unit quality in state $X$ (here we assume that $e_I>e_S$ to account for disease-induced mortality), and $\alpha$ controls how extinction rate scales with patch quality.  When an infectious population goes extinct, we assume that the infectious hosts leave behind an infectious pathogen reservoir on the patch.

Susceptible populations are infectious via direct contact with infectious colonists at rate $\delta C_{Ii}$, where $\delta$ is the transmission probability.  In addition, environmental transmission can take place when a susceptible population occupies a patch with an environmental reservoir, and occurs at rate:
\begin{equation}
\gamma_i=\gamma_0exp(-rt_{Ii}),
\end{equation}
where $\gamma_0$ is the initial infection rate of the pathogen reservoir, $t_{Ii}$ is the time since last infectious occupancy, and $r$ is the pathogen's decay rate in the environment.

\begin{table}[h!]
\label{parameters}      
\caption{Parameters of SPOM model and their interpretations.}
\begin{tabular}{l p{8.5cm} r}
Parameter & Interpretation &  Default Value\\
\hline
$\xi_{im}$ & Scaling parameter for effect of target patch quality on immigration & 0.5\\
$\xi_{em}$ & Scaling parameter for effect of target patch quality in emigration & 0.5\\
$D$& Inverse of mean dispersal distance & 5\\
$d_{ij}$ & Distance between patch $i$ and $j$ & 1 for all $i,j$\\
\hline
$e_S$ & Extinction rate of unit quality susceptible patch & 0.1\\
$e_I$ & Extinction rate of unity quality infectious patch & 0.5\\
$\alpha$ & Strength of environmental stochasticity & 1\\
\hline
$\delta$ & Probability of direct infection & 0.5\\
$\gamma_0$ & Initial rate of infection from reservoir patch & 0.5
\end{tabular}
\end{table}

\subsection{Model Implementation and Analysis}

The model outlined above was parameterized (Table 1) according to the following assumptions. (1) High quality patches maintain higher population sizes and therefore produce more colonists than low quality patches and have lower extinction rates than low quality patches ($\xi_{im}=0.5$, $\alpha=1$, \cite{Hanski2003}).  (2) High quality patches attract more colonists than low quality patches ($\xi_{em}=0.5$, \cite{Hanski2003}).  (3)  Connectivity among patches is determined entirely by quality ($d_{ij}=1$ for all $i \neq j$).  In addition to these assumptions, parameters were chosen so that without infection, approximately 0.75 of the metapopulation was occupied ($e_S = 0.1$, $D=5$), and a range of epidemiological behaviors -- disease-free, endemic disease, and pandemic disease (i.e. all host populations infectious) -- was feasible, depending on the pathogen's environmental longevity ($e_I = 0.5$, $\delta = 0.5$, $\gamma_0 = 0.5$).

With the above parameters fixed, we explored the effects of pathogen environmental persistence and habitat heterogeneity by varying pathogen longevity (10 values ranging from 20 to 200 time steps, with values representing the half-life of the pathogen's infectivity), and the variance of the patch quality distribution (10 values ranging from 0.02 to 0.2).  For each simulation (100 replicates for each of the 100 longevity-variance combinations), qualities for 100 patches were drawn from a uniform distribution with mean 1 and given variance. In each case, an entirely susceptible population was simulated until it reached an approximate steady state, at which point a randomly chosen occupied patch was infectious.  The state of the metapopulation was then tracked for 5000 time steps.  To address the metapopulation-level questions above, we recorded the proportion of patches in each state at the end of each simulation and classified the simulation as host extinction, disease-free (no infectious populations after 5000 time steps), endemic (both susceptible and infectious populations present), or pandemic (only infectious populations).  In addition, to address patch-level questions, for every simulation, we recorded the quality of each patch, the proportion of time spent in each state, and the number of transitions between each state.

In the above simulations, the mean of the patch quality distribution was held constant, and thus the range was expanded symmetrically about one as the variance was increased.  To further parse out the relative roles of high and low quality patches, we performed a series of simulations where we expanded the range of the quality distribution non-symmetrically to include high and low quality patches separately.  For these simulations, at each value for longevity, we simulated 100 metapopulations for each of four patch quality distributions: low varaince, (range 0.75 to 1.25); intermediate variance, high quality (range 0.75 to 1.75); intermediate variance, low quality (range 0.25 to 1.25); and high variance (range 0.25 to 1.75).

In addition, to explore the effects of the model assumptions and parameterization, we repeated the above analyses for three additional model parameterizations.  The focal model assumes that all patches are equally accessible from all other patches, so to examine the effects of a more rigid spatial structure, we implemented a model with patches arranged in a lattice structure.  In addition, we explored a model with $\alpha = 0$ so that the extinction rate was constant with patch quality, simulating the effecs of high environmental stochasticity (i.e. environmental stochasticity is strong enough that the population size of a patch does not affects its extinction rate).  Lastly, we parameterized a model with $\delta = 0.1$ to reduce the relative importance of direct transmission and explore the disease dynamics when transmission is driven largely by the environmental reservoir.

Continuous time stochastic simulations of the above model were implemented in the R language (citation) using the Gillespie algorithm (\cite{Gillespie1977}).  Code is available at \url{https://github.com/clint-leach/Metapop-Disease}.

@@

The pathogen persisted in 70$\%$ of the 10000 simulations, spreading through the entire susceptible host population (i.e. a pandemic) in 37$\%$ of the simulations.  Pathogen persistence increased substantially with longevity, with intermediate longevities favoring endemic disease, and high longevities facilitating pandemic dynamics (Fig~ \ref{poutcome}).  The effect of longevity, however, depended on the variance of the patch quality distribution, with low variance metapopulations favoring endemic dynamics for a wider range of longevities (Fig~ \ref{poutcome}a), and high variance metapopulations lowering the longevity required for pandemic dynamics (Fig~ \ref{poutcome}b).  The three alternative parameterizations (lattice structure, $\alpha = 0$, $\delta = 0.1$) produced qualitatively similar results, though pathogen spread in these models was generally more difficult (i.e. fewer pandemics), and the habitat quality variance exerted a relatively weaker influence on the epidemiological outcome (Figs~\ref{poutcome_lattice}, \ref{poutcome_x0}, \ref{poutcome_delta}).

\begin{figure}
\centering
\includegraphics[height=5.5cm]{metapop(full).pdf}
\caption{Percent of simulations resulting in (a) endemic disease (both susceptibles and infectiouss persist) and (b) pandemic disease (no susceptibles persist), as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome}
\end{figure}

@@

The positive relationship between pathogen spread and environmental longevity demonstrated in the theoretical model above is well documented in models of empirical systems.  Using a model parameterized for chronic wasting disease in mule deer, \cite{Almberg2011} find that increasing prion survival in the environment increases the resulting force of infection and peak prevalence, with the importance of reservoir transmission increasing through time.  Similarly, \cite{Breban2009} show that environmental transmission of avian influenza virus allows it to persist in situations where direct transmission alone is insufficient.  \emph{Other examples.}  Look into George et al (2013).

@@

\emph{Emphasize own results relative to the contact network literature.  Should try to avoid the "main model results suggest X, but sensitivity analysis models suggest Y" format and instead try to present a more complete picture/story.  In the primary model, the increase in pathogen spread from high variance metapopulations likely results from the presence of high quality patches and their ability to overwhelm low quality patches at high longevity through a combination of their relative stability, the high connectivity due to the uniform spatial structure, and the relative strength of direct infection.  The assumptions tested in the other models all weaken these effects -- by constraining movement through the lattice structure; by limiting the influence of direct infection and thus the influence of colonists from infected high quality patches; and by reducing the stability of high quality patches relative to low -- thus preventing low quality patches from being overwhelmed by the high quality patches.}

@@

\emph{High qualily patches also experience more infection events because they are able to support susceptibles long enough for them to get infected, whereas susceptibles on low quality patches are probably going to go extinct before they can become infected (though the effect persists when $\alpha = 0$ and is substantially diminished in the lattice model and when $\delta = 0.1$, so it seems that it is driven largely by connectivity and direct infection}

@@

Though this model provides evidence that high quality patches can serve as traps and superspreaders, and low quality patches can serve as susceptible refuges, the effects of these processes on total metapopulation occupancy depend on the strength and structure of the two transmission pathways.  \emph{Need more here?}  In particular, these findings suggest the presence of a trade-off between facilitating metapopulation stability and inhibiting disease spread, with a pathogen's environmental longevity and ease of spread controlling the roles of different quality patches with respect to this trade-off.  When pathogen spread is limited or slow (e.g. due to low longevity, or weak direct transmission), high quality patches are a net benefit to the metapopulation, as their connectivity and stability facilitate greater occupancy.

\emph{Maybe lay out the big picture in this paragraph: that there are essentially three different scenarios, very low pathogen spread, intermediate/endemic pathogen spread, and easy/pandemic pathogen spread and then go through each one and its consequences on the roles played by high and low quality habitat.}

@@

\emph{What does this model offer beyond the literature cited?  WRT Hess 1996, the extension to explicit habitat patches offers insight into the roles of specific patches; even though connectivity is an important driving factor in this model, it also allows us to consider the role of other processes (e.g. extinction, explicity pathogen transmission in space).}

@@

\emph{As with the notes above, emphasize not just how this work fits with other literature, but also what it adds.  WRT these other metapop disease modeling papers, may not want to equate increased patch quality with increased movement so easily and instead delve more into what including patch quality offers us.  "This refelcts the the results of blah in that ..., but offers the additional insight that ..."}

@@

\emph{Again, use this last paragraph not just to summarize the results, but to emphasize the novelty of these insights.}

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{color}

@@

Many wildlife diseases are caused by pathogens that can persist, and remain infectious, for long periods of time in the environment.  Examples include chronic wasting disease (\cite{Miller2006}), anthrax (\cite{Dragon1995}), plague (\cite{Eisen2008}), and white nose syndrome (\cite{Lindner2011}), among others.  This environmental persistence creates environmental pathogen reservoirs from which hosts can become infected without direct contact with an infectious individual.  This additional transmission pathway can have important consequences for disease dynamics, with models showing that increased environmental persistence generally facilitates increased pathogen persistence and spread relative to direct transmission alone (\cite{Almberg2011}, \cite{Sharp2011}, \cite{Breban2009}).

@@

\subsection{Model Structure}

\begin{table}
\caption{State transitions and their rates for patch $i$ in a metapopulation simulation.  $S$ denotes occupied by  susceptible hosts, $I$ denotes occupied infectious hosts, and $\emptyset$ denotes unoccupied by the host (but potentially with pathogen reservoir with infection rate of $\gamma_i$).}
\begin{tabular}{lr}
State Transition & Rate \\
\hline
$S \rightarrow I$ & $\delta C_{Ii} + \gamma_i$\\
$S \rightarrow \emptyset $ & $e_{Si}$\\
$I \rightarrow \emptyset $ & $e_{Ii}$ \\
$\emptyset \rightarrow S$ & $C_{Si}$\\
$\emptyset \rightarrow I$ & $C_{Ii}$\\
\label{transitions}
\end{tabular}
\end{table}

To address the above questions, we developed a theoretical stochastic patch occupancy model (SPOM) in which each patch can be in one of three possible states: occupied by susceptible hosts (S), occupied by infectious hosts (I), and unoccupied by the host ($\emptyset$).  State transitions are governed by host colonization, extinction, and infection rates, where a susceptible population can become infectious either through direct contact with infectious immigrants, or through a local pathogen reservoir (Table~\ref{transitions}).

@@

The extinction rate of patch $i$ in state $X$ is given by:
\begin{equation}
E_{Xi}=\frac{e_X}{A_i^\alpha},
\end{equation}
where $e_X$ is the extinction rate of a patch of unit quality in state $X$ (here we assume that $e_I>e_S$ to account for disease-induced mortality), and $\alpha$ controls how extinction rate scales with patch quality.  When an infectious population goes extinct, we assume that the hosts leave behind an infectious pathogen reservoir on the patch.

Susceptible populations are infected via direct contact with infectious colonists at rate $\delta C_{Ii}$, where $\delta$ is the transmission probability.  In addition, environmental transmission can take place when a susceptible population occupies a previously infected patch, and occurs at rate:
\begin{equation}
\gamma_i=\gamma_0exp(-rt_{Ii}),
\end{equation}
where $\gamma_0$ is the initial infection rate of the pathogen reservoir, $t_{Ii}$ is the time since last infectious occupancy ($t_{Ii} = \infty$, and thus $\gamma_i = 0$, if the patch has never been occupied by infectious hosts), and $r$ is the pathogen's decay rate in the environment.

\begin{table}[h!]   
\caption{Parameters of SPOM model, their meaning, and the values assigned under different parameterizations.  Empty cells indicate same value as the default parameterization.}
\begin{tabular}{l p{5cm} rrrr}
Parameter & Interpretation &  Default & Lattice & Equal Ext. & Weak Direct Inf.\\
\hline
$\xi_{im}$ & Scaling parameter for effect of target patch quality on immigration & 0.5 & -- & -- & --\\
$\xi_{em}$ & Scaling parameter for effect of target patch quality in emigration & 0.5 & -- & -- & --\\
$D$& Inverse of mean dispersal distance & 5 & 2 & -- & --\\
$d_{ij}$ & Distance between patch $i$ and $j$ & 1 $\forall i \neq j$ & 1 $\forall i, j$ neighbors & -- & --\\
\hline
$e_S$ & Extinction rate of unit quality susceptible patch & 0.1 & -- & -- & --\\
$e_I$ & Extinction rate of unity quality infectious patch & 0.5 & -- & -- & --\\
$\alpha$ & Strength of environmental stochasticity & 1 & -- & 0 & --\\
\hline
$\delta$ & Probability of direct infection & 0.5 & -- & -- & 0.1\\
$\gamma_0$ & Initial rate of infection from reservoir patch & 0.5 & -- & -- & --
\end{tabular}
\label{params}
\end{table}

\subsection{Model Parameterization}

The model outlined above was parameterized in four different ways to explore the consequences of different assumptions (Table~\ref{params}).  The baseline model was parameterized  according to the following assumptions. (1) High quality patches maintain higher population sizes and therefore produce more colonists than low quality patches and have lower extinction rates than low quality patches ($\xi_{im}=0.5$, $\alpha=1$, \cite{Hanski2003}).  (2) High quality patches attract more colonists than low quality patches ($\xi_{em}=0.5$, \cite{Hanski2003}).  (3)  Connectivity among patches is determined entirely by quality ($d_{ij}=1$ for all $i \neq j$).  In addition to these assumptions, parameters were chosen so that without infection, approximately 0.75 of the metapopulation was occupied ($e_S = 0.1$, $D=5$), and a range of epidemiological behaviors -- disease-free, endemic disease, and pandemic disease (i.e. all host populations infectious) -- was feasible, depending on the pathogen's environmental longevity ($e_I = 0.5$, $\delta = 0.5$, $\gamma_0 = 0.5$).

The baseline model above assumes that all patches are equally accessible from all other patches (i.e. are separated by distance 1), so to examine the effects of a more rigid spatial structure, we implemented a model with patches arranged in a square lattice such that each patch is only accessible from its four neighboring patches (Lattice, Table~\ref{params}).  In addition, we explored a model with $\alpha = 0$ so that the extinction rate was constant with patch quality, simulating the effects of high environmental stochasticity (i.e. environmental stochasticity is strong enough that the population size of a patch does not affects its extinction rate)(Equal extinction, Table~\ref{params}).  Lastly, we parameterized a model with $\delta = 0.1$ to reduce the relative importance of direct transmission and explore the disease dynamics when transmission is driven largely by the environmental reservoir (Weak direct infection, Table~\ref{params}).

\subsection{Simulation studies}

For each of the above parameterizations, we performed two different simulation experiments to explore the combined effects of pathogen environmental longevity and habitat quality distribution on disease dynamics and metapopulation occupancy.  In the first of these, we investigated the effect of increasing habitat heterogeneity on the dynamics of pathogens with a range of environmental longevities.  For these simulations, we explored 10 values of pathogen longevity ranging from 20 to 200 time steps, with values representing the half-life of the pathogen's infectivity, and 10 values for the variance of the patch quality distribution, ranging from 0.02 to 0.2.  For each simulation (100 replicates for each of the 100 longevity-variance combinations), qualities for 100 patches were drawn from a uniform distribution with fixed mean 1 and given variance. In each case, an entirely susceptible population was simulated until it reached an approximate steady state, at which point a randomly chosen occupied patch was infected.  The state of the metapopulation was then tracked for 5000 time steps.  We recorded the proportion of patches in each state at the end of each simulation and classified the simulation as host extinction, disease-free (no infectious populations after 5000 time steps), endemic (both susceptible and infectious populations present), or pandemic (only infectious populations).  In addition, to identify the roles played by individual patches of varying quality, for every simulation, we recorded the quality of each patch, the proportion of time spent in each state (i.e. occupied by susceptible hosts, occupied by infectious hosts, and unoccupied), and the number of transitions between each state.

The above simulations held the mean of patch quality distribution constant, and explored the effect of increasing habitat heterogeneity around that mean (i.e. by expanding the quality distribution symmetrically about 1).  To further parse out the relative influence of high and low quality patches separately, we performed a second series of simulations where we expanded the range of the uniform quality distribution to skew towards either high or low quality patches (i.e. by expanding the quality distribution non-symmetrically about 1).  For these simulations, at each of the 10 longevities used above, we simulated 100 metapopulations for each of four patch quality distributions: low variance, (patch qualities ranging 0.75 to 1.25); intermediate variance, high quality (range 0.75 to 1.75); intermediate variance, low quality (range 0.25 to 1.25); and high variance (range 0.25 to 1.75).

Continuous time stochastic simulations of the above model were implemented in the R language (\cite{R2014}) using the Gillespie algorithm (\cite{Gillespie1977}).  Code is available at \url{https://github.com/clint-leach/Metapop-Disease}.

@@

\textcolor{red}{Similar to above edits to methods, need to better distinguish the different analyses and what they're testing.}

The pathogen persisted in 70$\%$ of the 10000 simulations in the baseline model with symmetric patch quality distributions, spreading through the entire susceptible host population (i.e. a pandemic) in 37$\%$ of the simulations.  Pathogen persistence increased substantially with longevity, with intermediate longevities favoring endemic disease, and high longevities facilitating pandemic dynamics (Fig~ \ref{poutcome}).  The effect of longevity, however, depended on the variance of the patch quality distribution, with low variance metapopulations favoring endemic dynamics for a wider range of longevities (Fig~ \ref{poutcome}a), and high variance metapopulations lowering the longevity required for pandemic dynamics (Fig~ \ref{poutcome}b).  The three alternative parameterizations (lattice structure, $\alpha = 0$, $\delta = 0.1$) produced qualitatively similar results, though pathogen spread in these models was generally more difficult (i.e. fewer pandemics), and the habitat quality variance exerted a relatively weaker influence on the epidemiological outcome (Figs~\ref{poutcome_lattice}, \ref{poutcome_x0}, \ref{poutcome_delta}).

\begin{figure}
\centering
\includegraphics[height=5.5cm]{metapop(full).pdf}
\caption{Percent of simulations resulting in (a) endemic disease (both susceptibles and infectious hosts persist) and (b) pandemic disease (no susceptibles persist), as a function of the pathogen's environmental longevity (half-life of infectivity decay) and the variance of the patch quality distribution.}
\label{poutcome}
\end{figure}

@@

\textcolor{red}{Need to emphasize novelty of this work, especially compared to Hess, Gog, and Park.  Discuss that movement in this model is not only heterogeneous, but also directional and what that means.  Also consider reorganizing to put the more interesting elements at the front, and get rid of the less interesting parts (i.e. the first paragraph).  As with notes for results and methods, need to be clear about which analyses support which claims, and specifically need to be careful about discussing the different patch quality distributions and distinguishing between the symmetric and asymmetric distributions.}

The positive relationship between pathogen spread and environmental longevity demonstrated in the theoretical model above is well documented in models of empirical systems.  Using a model parameterized for chronic wasting disease in mule deer, \cite{Almberg2011} find that increasing prion survival in the environment increases the resulting force of infection and peak prevalence, with the importance of reservoir transmission increasing through time.  Similarly, \cite{Breban2009} show that environmental transmission of avian influenza virus allows it to persist in situations where direct transmission alone is insufficient.  \textcolor{red}{Other examples.}  Look into George et al (2013).

@@

\textcolor{red}{Emphasize own results relative to the contact network literature.  Should try to avoid the "main model results suggest X, but sensitivity analysis models suggest Y" format and instead try to present a more complete picture/story.  In the primary model, the increase in pathogen spread from high variance metapopulations likely results from the presence of high quality patches and their ability to overwhelm low quality patches at high longevity through a combination of their relative stability, the high connectivity due to the uniform spatial structure, and the relative strength of direct infection.  The assumptions tested in the other models all weaken these effects -- by constraining movement through the lattice structure; by limiting the influence of direct infection and thus the influence of colonists from infected high quality patches; and by reducing the stability of high quality patches relative to low -- thus preventing low quality patches from being overwhelmed by the high quality patches.}

@@

\textcolor{red}{High qualily patches also experience more infection events because they are able to support susceptibles long enough for them to get infected, whereas susceptibles on low quality patches are probably going to go extinct before they can become infected (though the effect persists when $\alpha = 0$ and is substantially diminished in the lattice model and when $\delta = 0.1$, so it seems that it is driven largely by connectivity and direct infection}

@@

Though this model provides evidence that high quality patches can serve as traps and superspreaders, and low quality patches can serve as susceptible refuges, the effects of these processes on total metapopulation occupancy depend on the strength and structure of the two transmission pathways.  \textcolor{red}{Need more here?}  In particular, these findings suggest the presence of a trade-off between facilitating metapopulation stability and inhibiting disease spread, with a pathogen's environmental longevity and ease of spread controlling the roles of different quality patches with respect to this trade-off.  When pathogen spread is limited or slow (e.g. due to low longevity, or weak direct transmission), high quality patches are a net benefit to the metapopulation, as their connectivity and stability facilitate greater occupancy.

\textcolor{red}{Maybe lay out the big picture in this paragraph: that there are essentially three different scenarios, very low pathogen spread, intermediate/endemic pathogen spread, and easy/pandemic pathogen spread and then go through each one and its consequences on the roles played by high and low quality habitat.}

@@

\textcolor{red}{What does this model offer beyond the literature cited?  WRT Hess 1996, the extension to explicit habitat patches offers insight into the roles of specific patches; even though connectivity is an important driving factor in this model, it also allows us to consider the role of other processes (e.g. extinction, explicity pathogen transmission in space).}

@@

\textcolor{red}{As with the notes above, emphasize not just how this work fits with other literature, but also what it adds.  WRT these other metapop disease modeling papers, may not want to equate increased patch quality with increased movement so easily and instead delve more into what including patch quality offers us.  "This refelcts the the results of blah in that ..., but offers the additional insight that ..."}

@@

\textcolor{red}{Again, use this last paragraph not just to summarize the results, but to emphasize the novelty of these insights.}
